Learning constraints in tabular data

### 2016-05-11 Paper/ECAI/tabular.tex
fixed all links in the intro

The approach that we will introduce will borrow techniques from logical and relational learning \cite{LucBook}, where
\cite{Claudien,todo:lallouet} have studied the discovery of clausal constraints in an inductive logic programming setting, from constraint learning,  where \cite{Quacq,Conacq,Modelseeker} have developed several approaches to learn conjunctive constraints in a constraint programming setting,
and from mining in databases,  where e.g. \cite{Savlik} has applied inductive techniques to discover constraints (such as functional and multi-valued dependencies) in relational databases.  It also builds on work on program synthesis, in particular, on Flashfill \cite{}, where the definition of function is learned in spreadsheet data from
very few examples.  Our approach contrasts with all of the mentioned approaches (except Modelseeker) in that it focusses
on learning both column- and row-constraints, it contrasts with Flashfill in learning constraints rather than functions.
A more detailed discussion on related work is contained in Section \luc{TODO}.

@@

\item the \textit{\CSignature} defines the properties that the arguments of the predicate must satisfy. That is, the required types of the arguments, together
with possible further restrictions, e.g., on their length. For example, the signature can restrict the types of the arguments to be groups of integers and require that the length of all arguments be equal. \\
In terms of logical and relational learning \cite{bookLuc}, such a \CSignature is known as the {\em bias} of the learner, it specifies when the constraint is well-formed.

@@

Depending on the application, a solution to the tabular constraint learning problem may contain \textit{redundant} constraints, cf. \cite{bookLuc}. This is because constraints may be logically equivalent or may be implied by other constraints.

@@

\section{Related Work}
\sergey{key bullet points for Luc and possibly Samuel and me to make related work section}

>>>>

The approach that we will introduce will borrow techniques from logical and relational learning \cite{luc_book}, where
\cite{claudien,lallouet} have studied the discovery of clausal constraints in an inductive logic programming setting, from constraint learning,  where \cite{Quacq,Conacq,modelseeker} have developed several approaches to learn conjunctive constraints in a constraint programming setting,
and from mining in databases,  where e.g. \cite{Shavlik} has applied inductive techniques to discover constraints (such as functional and multi-valued dependencies) in relational databases.  It also builds on work on program synthesis, in particular, on Flashfill \cite{flashfill}, where the definition of function is learned in spreadsheet data from
very few examples.  Our approach contrasts with all of the mentioned approaches (except Modelseeker) in that it focusses
on learning both column- and row-constraints, it contrasts with Flashfill in learning constraints rather than functions.
A more detailed discussion on related work is contained in Section \ref{sec:related_work}.

@@

\item the \textit{\CSignature} defines the properties that the arguments of the predicate must satisfy. That is, the required types of the arguments, together
with possible further restrictions, e.g., on their length. For example, the signature can restrict the types of the arguments to be groups of integers and require that the length of all arguments be equal. \\
In terms of logical and relational learning \cite{luc_book}, such a \CSignature is known as the {\em bias} of the learner, it specifies when the constraint is well-formed.

@@

Depending on the application, a solution to the tabular constraint learning problem may contain \textit{redundant} constraints, cf. \cite{luc_book}. This is because constraints may be logically equivalent or may be implied by other constraints.

@@

\section{Related Work}\label{sec:related_work}
\sergey{key bullet points for Luc and possibly Samuel and me to make related work section}
